DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-07-02 ase2017/paper.tex
wording

Notably, there are toolboxes in MATLAB with functions and scripts to
facilitate the digital system design and
implementation~\cite{matlab-toolbox}.  Indeed, there is a MATLAB Toolbox
named as DSVerifier
Toolbox~\cite{issta2017,DBLP:journals/tc/BessaIPCF17,DBLP:journals/dafes/BessaICF16},
which automatically detects specific errors related to digital system design
({\it e.g.}, stability, limit cycle and overflow) using symbolic model
checking techniques based on Boolean Satisfiability (SAT) and Satisfiability
Modulo Theories (SMT) solvers.  Pessoa~\cite{mazo2010pessoa} is another
toolbox, but applied to the synthesis of correct-by-design digital
controllers.  In particular, Pessoa is based on approximate bisimulation,
which allows control engineers to replace differential equations, describing
a physical plant, by a respective finite-state machine.  However, Pessoa
does not take advantage of recent advances in bit-accurate verification of
programs to synthesize controllers w.r.t.  FWL effects.  MATLAB already
offers a tool named as Control System Tuner~\cite{autotuner} for
automatically designing controllers based on optimization solvers or
graphical analysis.  However, the Control System Tuner is unable to consider
FWL effects during the controller synthesis process.  To the best of our
knowledge, there is no MATLAB toolbox able to perform digital controller
synthesis based on program synthesis engines that considers the complete
range of approximations, including time discretization, quantization
effects, and finite-precision arithmetic and its rounding errors.

>>>>

There are existing toolboxes for MATLAB that provide functions and scripts
to support design and implementation of digital
controllers~\cite{matlab-toolbox}.  In~particular, there is a MATLAB Toolbox
named \emph{DSVerifier}~\cite{issta2017, DBLP:journals/tc/BessaIPCF17,
DBLP:journals/dafes/BessaICF16}, which automatically detects specific errors
in a given digital system design (e.g., errors related to stability, limit
cycle and overflow) using symbolic model checking based on Boolean
Satisfiability (SAT) and Satisfiability Modulo Theories (SMT) solvers.  The
Pessoa~\cite{mazo2010pessoa} toolbox performs synthesis of correct-by-design
digital controllers.  Pessoa is based on approximate bisimulation, which
allows control engineers to replace differential equations, describing a
physical plant, by a respective finite-state machine.  However, Pessoa does
not take advantage of recent advances in bit-accurate verification of
programs to synthesize controllers w.r.t.~FWL effects.  MATLAB 
offers a tool named Control System Tuner~\cite{autotuner} for
automatically designing controllers based on optimization solvers or
graphical analysis.  However, the Control System Tuner is unable to consider
FWL effects during the controller synthesis process.  To the best of our
knowledge, there is no MATLAB toolbox able to perform digital controller
synthesis based on program synthesis engines that considers the complete
range of approximations, including time discretization, quantization
effects, and finite-precision arithmetic and its rounding errors.
